Effect of Black Hole Spin on Christodoulou Memory

### 2019-02-12 notes/Paper.tex
updated paper

\begin{figure}
 	\includegraphics[width=4.0in]{../plots/MemoryPlot_nonSpining/q7.pdf}
 	\caption{The figure above shows Christodoulou memory as a function of time during BBH coalesce. This figure shows a comparison for different mass ratios. It can be seen that higher mass ration tends to decrease the Chistodoulou memory. The early inspiral part is computed using post-Newtonian expression and the later part during BBH merger is computer using Numerical Relativity data. The red dashed line shows result from PN expression}
 	\label{fig:differentmassratio}
\end{figure}
\begin{figure}
	\includegraphics[width=3.5in]{../plots/MemoryPlot_AlignedSpinSXSdata/0p99.pdf}
	\includegraphics[width=3.5in]{../plots/MemoryPlot_AntialignedSpinSXSdata/m0p94.pdf}
	\caption{The figure above shows Christodoulou memory as a function of time during BBH coalesce. The top figure shows a comparison for different values of dimensionless spin parameter $\chi$. These results are for BBH system with equal spin magnitude for individual black hole and spins aligned with orbital angular momentum. It can be seen that higher spin magnitude tend to increase the Christodoulou memory. The bottom figure shows the anti aligned case.  }
	\label{fig:differntchivalues}
\end{figure}

>>>>

\begin{figure}
 	\includegraphics[width=4.0in]{../plots/MemoryPlot_nonSpining/q7.pdf}
 	\caption{The figure above shows Christodoulou memory as a function of time during BBH coalesce. This figure shows a comparison for different mass ratios. It can be seen that higher mass ration tends to decrease the Chistodoulou memory. The early inspiral part is computed using post-Newtonian expression and the later part during BBH merger is computer using Numerical Relativity data. The red dashed line shows result from PN expression}
 	\label{fig:differentmassratio}
\end{figure}
\begin{figure}
	\includegraphics[width=4.0in]{../plots/MemoryPlot_AlignedSpinSXSdata/0p99.pdf}
	\includegraphics[width=4.0in]{../plots/MemoryPlot_AntialignedSpinSXSdata/m0p94.pdf}
	\caption{The figure above shows Christodoulou memory as a function of time during BBH coalesce. The top figure shows a comparison for different values of dimensionless spin parameter $\chi$. These results are for BBH system with equal spin magnitude for individual black hole and spins aligned with orbital angular momentum. It can be seen that higher spin magnitude tend to increase the Christodoulou memory. The bottom figure shows the anti aligned case.  }
	\label{fig:differntchivalues}
\end{figure}
